---
title: "do_plots"
author: "Xiao Chen"
date: "2024-07-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data

load the benchmark results

```{r load data}
rm(list = ls())
cat("\014")

library(wesanderson)
library(gtsummary)
library(officer)
library(readxl)
library(dplyr)

work_dir <- "/Users/ChenXiao/Library/CloudStorage/OneDrive-Personal/Documents/scale_crosswalk/Analysis"
output_dir <- "/Users/ChenXiao/Library/CloudStorage/OneDrive-Personal/Documents/scale_crosswalk/plots_MR"

# Check if the path exists
if (!file.exists(output_dir)) {
  # If it doesn't exist, create the directory
  dir.create(output_dir, recursive = TRUE)
  message("Directory created.")
} else {
  message("Directory already exists.")
}

load(file.path(work_dir, "benchmarks_ALL_carryover241205.RData"))
benchmarks_HAMD2MADRS <- df_rmse
load(file.path(work_dir, "benchmarks_M2H_ALL_carryover241205.RData"))
benchmarks_MADRS2HAMD <- df_rmse

custom_colors <- c("PEM (benchmark)" = "#6C946F", "Linear Regression" = "#D4BDAC", "rTMS Equipercentile Model" = "#FFA823", "RF Regression" = "#DC0083", "SVR" = "#536493", "SVR Item" = "#8CB9BD", "SVR Cov" = "#E7F0DC", "SVR Item Cov" = "#B6C7AA")
```

## Primary figure

organize data

```{r organize data}

data_matrix <- matrix(0, nrow = 5, ncol = 3)
colnames(data_matrix) <- c("Baseline", "T30", "Delta")
rownames(data_matrix) <- c("PEM (benchmark)", "rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR")

temp <- 0
for (i in c(1,2,10)){
  temp <- temp + 1
  selected_values <- benchmarks_HAMD2MADRS[c(1,2,3,5,7),i]
  data_matrix[, temp] = selected_values
}
# to make bar plots
df_H2M <- as.data.frame(data_matrix)
df_H2M$Group <- "HAMD to MADRS"

data_matrix <- matrix(0, nrow = 5, ncol = 3)
colnames(data_matrix) <- c("Baseline", "T30", "Delta")
rownames(data_matrix) <- c("PEM (benchmark)", "rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR")

temp <- 0
for (i in c(1,2,10)){
  temp <- temp + 1
  selected_values <- benchmarks_MADRS2HAMD[c(1,2,3,5,7),i]
  data_matrix[, temp] = selected_values
}

df_M2H <- as.data.frame(data_matrix)
df_M2H$Group <- "MADRS to HAMD"
```

## Another set of bar plots

This version is used

```{r}

library(tidyr)
library(tidyverse)
library(ggplot2)


df_full <- rbind(df_H2M,df_M2H)
selected_columns = df_full[, c('Baseline', 'T30', 'Delta')]
max_value <-  max(selected_columns)

my_height <-  8
my_width <- 14

df_H2M$Group <- NULL
df_H2M$Models <- rownames(df_H2M)
rownames(df_H2M) <- 1:nrow(df_H2M)

# Add a placeholder row for spacing
placeholder <- data.frame(
  Baseline = 0,
  T30 = 0,
  Delta = 0,
  Models = "Spacer"
)
# Combine the original dataset with the placeholder
df_H2M <- bind_rows(df_H2M, placeholder)

df_long <- df_H2M %>% 
  pivot_longer(cols = c("Baseline", "T30", "Delta"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "T30", "Baseline"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR", "Spacer", "PEM (benchmark)"), ordered = TRUE)
# df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))

ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.75) +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "primary_H2M_spaced_legend_v2.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)

df_M2H$Group <- NULL
df_M2H$Models <- rownames(df_M2H)
rownames(df_M2H) <- 1:nrow(df_M2H)

# Combine the original dataset with the placeholder
df_M2H <- bind_rows(df_M2H, placeholder)

df_long <- df_M2H %>% 
  pivot_longer(cols = c("Baseline", "T30", "Delta"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "T30", "Baseline"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR", "Spacer", "PEM (benchmark)"), ordered = TRUE)
# df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))

ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.75) +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "primary_M2H_spaced_v2_legend.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)
```

## Supplementary Figure 1

organize data

```{r organize data}

data_matrix <- matrix(0, nrow = 5, ncol = 3)
colnames(data_matrix) <- c("Follow-up 1", "Follow-up 2", "Follow-up 3")
rownames(data_matrix) <- c("PEM (benchmark)", "rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR")

temp <- 0
for (i in c(4,6,8)){
  temp <- temp + 1
  selected_values <- benchmarks_HAMD2MADRS[c(1,2,3,5,7),i]
  data_matrix[, temp] = selected_values
}

df_H2M <- as.data.frame(data_matrix)
df_H2M$Group <- "HAMD to MADRS"

data_matrix <- matrix(0, nrow = 5, ncol = 3)
colnames(data_matrix) <- c("Follow-up 1", "Follow-up 2", "Follow-up 3")
rownames(data_matrix) <- c("PEM (benchmark)", "rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR")

temp <- 0
for (i in c(4,6,8)){
  temp <- temp + 1
  selected_values <- benchmarks_MADRS2HAMD[c(1,2,3,5,7),i]
  data_matrix[, temp] = selected_values
}

df_M2H <- as.data.frame(data_matrix)
df_M2H$Group <- "MADRS to HAMD"
```

## Plot bar plots instead

This version is used

```{r}
library(tidyverse)


df_full <- rbind(df_H2M,df_M2H)
selected_columns = df_full[, c("Follow-up 1", "Follow-up 2", "Follow-up 3")]
max_value <-  max(selected_columns)

my_height <-  8
my_width <- 14

df_H2M$Group <- NULL
df_H2M$Models <- rownames(df_H2M)
rownames(df_H2M) <- 1:nrow(df_H2M)

# Add a placeholder row for spacing
placeholder <- data.frame(
  Baseline = 0,
  T30 = 0,
  Delta = 0,
  Models = "Spacer"
)
# Combine the original dataset with the placeholder
df_H2M <- bind_rows(df_H2M, placeholder)

df_long <- df_H2M %>% 
  pivot_longer(cols = c("Follow-up 1", "Follow-up 2", "Follow-up 3"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Follow-up 3", "Follow-up 2", "Follow-up 1"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR", "Spacer", "PEM (benchmark)"), ordered = TRUE)
# df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))

ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.75) +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "folllowup_H2M_spaced_v2_legend.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)

df_M2H$Group <- NULL
df_M2H$Models <- rownames(df_M2H)
rownames(df_M2H) <- 1:nrow(df_M2H)

# Combine the original dataset with the placeholder
df_M2H <- bind_rows(df_M2H, placeholder)

df_long <- df_M2H %>% 
  pivot_longer(cols = c("Follow-up 1", "Follow-up 2", "Follow-up 3"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Follow-up 3", "Follow-up 2", "Follow-up 1"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR", "Spacer", "PEM (benchmark)"), ordered = TRUE)
# df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))


ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.75) +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "folllowup_M2H_spaced_v2_legend.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)
```

## Figure 2: baseline model predicting other time points

HAMD 2 MADRS

```{r}
data_matrix <- matrix(0, nrow = 4, ncol = 5)
colnames(data_matrix) <- c("T30", "Follow-up 1", "Follow-up 2", "Follow-up 3", "Delta")
rownames(data_matrix) <- c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR")

temp <- 0
for (i in c(3,5,7,9,11)){
  temp <- temp + 1
  selected_values <- benchmarks_HAMD2MADRS[c(2,3,5,7),i]
  data_matrix[, temp] = selected_values
}

# my_breaks <- seq(3, 11, length.out = 200)
# jet_colors <- colorRampPalette(c("blue", "cyan", "yellow", "red"))(length(my_breaks) - 1)
# png(file.path(output_dir, "/benchmark_HAMD2MADRS_baseline_model.png"), 
#     width = 6000, height = 5000, res = 1200)
# pheatmap(data_matrix,
#          display_numbers = TRUE,
#          number_color = "black",
#          breaks = my_breaks,
#          color = jet_colors,
#          fontsize_number = 14,
#          cluster_cols = FALSE,
#          cluster_rows = FALSE)
# dev.off()

# to make bar plots
df_H2M <- as.data.frame(data_matrix)
df_H2M$Group <- "HAMD to MADRS"
```

MADRS to HAMD

```{r}
data_matrix <- matrix(0, nrow = 4, ncol = 5)
colnames(data_matrix) <- c("T30", "Follow-up 1", "Follow-up 2", "Follow-up 3", "Delta")
rownames(data_matrix) <- c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR")

temp <- 0
for (i in c(3,5,7,9,11)){
  temp <- temp + 1
  selected_values <- benchmarks_MADRS2HAMD[c(2,3,5,7),i]
  data_matrix[, temp] = selected_values
}

# my_breaks <- seq(3, 11, length.out = 200)
# jet_colors <- colorRampPalette(c("blue", "cyan", "yellow", "red"))(length(my_breaks) - 1)
# png(file.path(output_dir, "benchmark_MADRS2HAMD_baseline_model.png"), 
#     width = 6000, height = 5000, res = 1200)
# pheatmap(data_matrix,
#          display_numbers = TRUE,
#          number_color = "black",
#          breaks = my_breaks,
#          color = jet_colors,
#          fontsize_number = 14,
#          cluster_cols = FALSE,
#          cluster_rows = FALSE)
# dev.off()

# to make bar plots
df_M2H <- as.data.frame(data_matrix)
df_M2H$Group <- "MADRS to HAMD"
```

## New horizontal bar plots

```{r}
library(tidyverse)

df_full <- rbind(df_H2M,df_M2H)
# selected_columns = df_full[, c('T30', 'Follow-up 1', 'Follow-up 2', 'Follow-up 3', 'Delta')]
selected_columns = df_full[, c('Follow-up 1', 'Follow-up 2', 'Follow-up 3')]
max_value <-  max(selected_columns)

my_height <-  8
my_width <- 14

df_H2M$Group <- NULL
df_H2M$Models <- rownames(df_H2M)
rownames(df_H2M) <- 1:nrow(df_H2M)

# df_long <- df_H2M %>% 
#   pivot_longer(cols = c('T30', 'Follow-up 1', 'Follow-up 2', 'Follow-up 3', 'Delta'),
#                names_to = "Time point",
#                values_to = "RMSE")
# df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "Follow-up 3", "Follow-up 2", 'Follow-up 1', 'T30'), ordered = TRUE)

df_long <- df_H2M %>% 
  pivot_longer(cols = c('Follow-up 1', 'Follow-up 2', 'Follow-up 3'),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Follow-up 3", "Follow-up 2", 'Follow-up 1'), ordered = TRUE)

df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))

ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "baseline_model_legend.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)

df_M2H$Group <- NULL
df_M2H$Models <- rownames(df_M2H)
rownames(df_M2H) <- 1:nrow(df_M2H)

# df_long <- df_M2H %>% 
#   pivot_longer(cols = c('T30', 'Follow-up 1', 'Follow-up 2', 'Follow-up 3', 'Delta'),
#                names_to = "Time point",
#                values_to = "RMSE")
# df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "Follow-up 3", "Follow-up 2", 'Follow-up 1', 'T30'), ordered = TRUE)

df_long <- df_M2H %>% 
  pivot_longer(cols = c('Follow-up 1', 'Follow-up 2', 'Follow-up 3'),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Follow-up 3", "Follow-up 2", 'Follow-up 1'), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "Linear Regression", "RF Regression", "SVR"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))

ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "baseline_model_M2H_v2.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)
```

## Trajectory plot

this figure was plotted using \~/traj_compare_v2.R

## Comparing using item scores or total scores

```{r HAMD to MADRS}
data_matrix <- matrix(0, nrow = 3, ncol = 3)
colnames(data_matrix) <- c("Baseline", "T30", "Delta")
rownames(data_matrix) <- c("rTMS Equipercentile Model", "SVR", "SVR Item")

temp <- 0
for (i in c(1,2,10)){
  temp <- temp + 1
  selected_values <- benchmarks_HAMD2MADRS[c(2,7,8),i]
  data_matrix[, temp] = selected_values
}

# my_breaks <- seq(3.5, 6.5, length.out = 200)
# jet_colors <- colorRampPalette(c("blue", "cyan", "yellow", "red"))(length(my_breaks) - 1)
# png(file.path(output_dir, "benchmark_HAMD2MADRS_Item.png"), 
#     width = 6000, height = 6000, res = 1200)
# pheatmap(data_matrix,
#          display_numbers = TRUE,
#          number_color = "black",
#          breaks = my_breaks,
#          color = jet_colors,
#          fontsize_number = 14,
#          cluster_cols = FALSE,
#          cluster_rows = FALSE)
# dev.off()

# to make bar plots
df_H2M <- as.data.frame(data_matrix)
df_H2M$Group <- "HAMD to MADRS"
```

MADRS to HAMD

```{r MADRS to HAMD}
data_matrix <- matrix(0, nrow = 3, ncol = 3)
colnames(data_matrix) <- c("Baseline", "T30", "Delta")
rownames(data_matrix) <- c("rTMS Equipercentile Model", "SVR", "SVR Item")

temp <- 0
for (i in c(1,2,10)){
  temp <- temp + 1
  selected_values <- benchmarks_MADRS2HAMD[c(2,7,8),i]
  data_matrix[, temp] = selected_values
}

# my_breaks <- seq(3.5, 6.5, length.out = 200)
# jet_colors <- colorRampPalette(c("blue", "cyan", "yellow", "red"))(length(my_breaks) - 1)
# png(file.path(output_dir, "benchmark_MADRS2HAMD_Item.png"), 
#     width = 6000, height = 6000, res = 1200)
# pheatmap(data_matrix,
#          display_numbers = TRUE,
#          number_color = "black",
#          breaks = my_breaks,
#          color = jet_colors,
#          fontsize_number = 14,
#          cluster_cols = FALSE,
#          cluster_rows = FALSE)
# dev.off()

# to make bar plots
df_M2H <- as.data.frame(data_matrix)
df_M2H$Group <- "MADRS to HAMD"
```

## Plot bar figure instead

```{r}
library(tidyverse)


df_full <- rbind(df_H2M,df_M2H)
selected_columns = df_full[, c("Baseline", "T30", "Delta")]
max_value <-  max(selected_columns)

my_height <-  8
my_width <- 12

df_H2M$Group <- NULL
df_H2M$Models <- rownames(df_H2M)
rownames(df_H2M) <- 1:nrow(df_H2M)

df_long <- df_H2M %>% 
  pivot_longer(cols = c("Baseline", "T30", "Delta"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "T30", "Baseline"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "SVR", "SVR Item"), ordered = TRUE)
# df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))


ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "Item_compare_legend.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)

df_M2H$Group <- NULL
df_M2H$Models <- rownames(df_M2H)
rownames(df_M2H) <- 1:nrow(df_M2H)

df_long <- df_M2H %>% 
  pivot_longer(cols = c("Baseline", "T30", "Delta"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "T30", "Baseline"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("rTMS Equipercentile Model", "SVM Regression", "SVM Regression Item"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))


ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "Item_compare_M2H_v2.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)
```

## Showing results with vs. without covs

```{r}
load(file.path(work_dir, "benchmarks_covariates.RData"))
data_matrix <- matrix(0, nrow = 4, ncol = 3)
colnames(data_matrix) <- c("Baseline", "T30", "Delta")
rownames(data_matrix) <- c("SVR", "SVR Cov", "SVR Item", "SVR Item Cov")

temp <- 0
for (i in c(1,2,10)){
  temp <- temp + 1
  selected_values <- df_rmse[c(9,10,11,12),i]
  data_matrix[, temp] = selected_values
}

# my_breaks <- seq(3.5, 6, length.out = 200)
# jet_colors <- colorRampPalette(c("blue", "cyan", "yellow", "red"))(length(my_breaks) - 1)
# png(file.path(output_dir, "benchmark_HAMD2MADRS_cov.png"), 
#     width = 6000, height = 6000, res = 1200)
# pheatmap(data_matrix,
#          display_numbers = TRUE,
#          number_color = "black",
#          breaks = my_breaks,
#          color = jet_colors,
#          fontsize_number = 14,
#          cluster_cols = FALSE,
#          cluster_rows = FALSE)
# dev.off()

# to make bar plots
df_H2M <- as.data.frame(data_matrix)
df_H2M$Group <- "HAMD to MADRS"
```

## Plot bar figures instead

```{r}
library(tidyverse)


selected_columns = df_H2M[, c("Baseline", "T30", "Delta")]
max_value <-  max(selected_columns)

my_height <-  8
my_width <- 12

df_H2M$Group <- NULL
df_H2M$Models <- rownames(df_H2M)
rownames(df_H2M) <- 1:nrow(df_H2M)

df_long <- df_H2M %>% 
  pivot_longer(cols = c("Baseline", "T30", "Delta"),
               names_to = "Time point",
               values_to = "RMSE")
df_long$`Time point` <- factor(df_long$`Time point`, levels = c("Delta", "T30", "Baseline"), ordered = TRUE)
df_long$Models <- factor(df_long$Models, levels = c("SVR", "SVR Cov", "SVR Item", "SVR Item Cov"), ordered = TRUE)
#df_long$Models <- factor(df_long$Models, levels = rev(levels(df_long$Models)))


ggplot(df_long, aes(x = `Time point`, y = RMSE, fill = Models)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(limits = c(0, ceiling(max_value)), breaks = seq(0, ceiling(max_value), by = 1)) +
  labs(title = "", x = "", y = "RMSE") +
  theme_classic() + coord_flip() +
  scale_fill_manual(values = custom_colors) +
  theme(plot.title = element_text(hjust = 0.5))

ggsave(file.path(output_dir, "Cov_compare_legend.png"), height = my_height, width = my_width, units = "cm", dpi = 1200)
```

## Table 1

```{r}
# read in data
file_path <- file.path(work_dir, "FOURD_CARTBIND_dataset.xlsx")
FOURD <- read_excel(file_path, sheet = "FOURD")
CARTBIND <- read_excel(file_path, sheet = "CARTBIND")

FOURD$BENZO[is.na(FOURD$BENZO)] <- 0
FOURD$ANTIDEP[is.na(FOURD$ANTIDEP)] <- 0
FOURD$ANTIDEP_COMB[is.na(FOURD$ANTIDEP_COMB)] <- 0

# To address the high missing rate of the baseline time point in FOURD dataset, 
# check if they are NA, if yes, carry over the screen data
FOURD$hrsd1s_b <- ifelse(is.na(FOURD$hrsd1s_b), FOURD$hrsd1s_s, FOURD$hrsd1s_b)
FOURD$hrsd2s_b <- ifelse(is.na(FOURD$hrsd2s_b), FOURD$hrsd2s_s, FOURD$hrsd2s_b)
FOURD$hrsd3s_b <- ifelse(is.na(FOURD$hrsd3s_b), FOURD$hrsd3s_s, FOURD$hrsd3s_b)
FOURD$hrsd4s_b <- ifelse(is.na(FOURD$hrsd4s_b), FOURD$hrsd4s_s, FOURD$hrsd4s_b)
FOURD$hrsd5s_b <- ifelse(is.na(FOURD$hrsd5s_b), FOURD$hrsd5s_s, FOURD$hrsd5s_b)
FOURD$hrsd6s_b <- ifelse(is.na(FOURD$hrsd6s_b), FOURD$hrsd6s_s, FOURD$hrsd6s_b)
FOURD$hrsd7s_b <- ifelse(is.na(FOURD$hrsd7s_b), FOURD$hrsd7s_s, FOURD$hrsd7s_b)
FOURD$hrsd8s_b <- ifelse(is.na(FOURD$hrsd8s_b), FOURD$hrsd8s_s, FOURD$hrsd8s_b)
FOURD$hrsd9s_b <- ifelse(is.na(FOURD$hrsd9s_b), FOURD$hrsd9s_s, FOURD$hrsd9s_b)
FOURD$hrsd10s_b <- ifelse(is.na(FOURD$hrsd10s_b), FOURD$hrsd10s_s, FOURD$hrsd10s_b)
FOURD$hrsd11s_b <- ifelse(is.na(FOURD$hrsd11s_b), FOURD$hrsd11s_s, FOURD$hrsd11s_b)
FOURD$hrsd12s_b <- ifelse(is.na(FOURD$hrsd12s_b), FOURD$hrsd12s_s, FOURD$hrsd12s_b)
FOURD$hrsd13s_b <- ifelse(is.na(FOURD$hrsd13s_b), FOURD$hrsd13s_s, FOURD$hrsd13s_b)
FOURD$hrsd14s_b <- ifelse(is.na(FOURD$hrsd14s_b), FOURD$hrsd14s_s, FOURD$hrsd14s_b)
FOURD$hrsd15s_b <- ifelse(is.na(FOURD$hrsd15s_b), FOURD$hrsd15s_s, FOURD$hrsd15s_b)
FOURD$hrsd16s_b <- ifelse(is.na(FOURD$hrsd16s_b), FOURD$hrsd16s_s, FOURD$hrsd16s_b)
FOURD$hrsd17s_b <- ifelse(is.na(FOURD$hrsd17s_b), FOURD$hrsd17s_s, FOURD$hrsd17s_b)
FOURD$hrsd_total_b <- ifelse(is.na(FOURD$hrsd_total_b), FOURD$hrsd_total_s, FOURD$hrsd_total_b)

# also carry over the madrs screen data to the baseline data in FOURD
FOURD$madrs1_b <- ifelse(is.na(FOURD$madrs1_b), FOURD$madrs1_s, FOURD$madrs1_b)
FOURD$madrs2_b <- ifelse(is.na(FOURD$madrs2_b), FOURD$madrs2_s, FOURD$madrs2_b)
FOURD$madrs3_b <- ifelse(is.na(FOURD$madrs3_b), FOURD$madrs3_s, FOURD$madrs3_b)
FOURD$madrs4_b <- ifelse(is.na(FOURD$madrs4_b), FOURD$madrs4_s, FOURD$madrs4_b)
FOURD$madrs5_b <- ifelse(is.na(FOURD$madrs5_b), FOURD$madrs5_s, FOURD$madrs5_b)
FOURD$madrs6_b <- ifelse(is.na(FOURD$madrs6_b), FOURD$madrs6_s, FOURD$madrs6_b)
FOURD$madrs7_b <- ifelse(is.na(FOURD$madrs7_b), FOURD$madrs7_s, FOURD$madrs7_b)
FOURD$madrs8_b <- ifelse(is.na(FOURD$madrs8_b), FOURD$madrs8_s, FOURD$madrs8_b)
FOURD$madrs9_b <- ifelse(is.na(FOURD$madrs9_b), FOURD$madrs9_s, FOURD$madrs9_b)
FOURD$madrs10_b <- ifelse(is.na(FOURD$madrs10_b), FOURD$madrs10_s, FOURD$madrs10_b)
FOURD$total_madrs_b <- ifelse(is.na(FOURD$total_madrs_b), FOURD$total_madrs_s, FOURD$total_madrs_b)

# carryover the CARTBIND data
CARTBIND$hrsd1s_b2 <- ifelse(is.na(CARTBIND$hrsd1s_b2), CARTBIND$hrsd1s_b1, CARTBIND$hrsd1s_b2)
CARTBIND$hrsd2s_b2 <- ifelse(is.na(CARTBIND$hrsd2s_b2), CARTBIND$hrsd2s_b1, CARTBIND$hrsd2s_b2)
CARTBIND$hrsd3s_b2 <- ifelse(is.na(CARTBIND$hrsd3s_b2), CARTBIND$hrsd3s_b1, CARTBIND$hrsd3s_b2)
CARTBIND$hrsd4s_b2 <- ifelse(is.na(CARTBIND$hrsd4s_b2), CARTBIND$hrsd4s_b1, CARTBIND$hrsd4s_b2)
CARTBIND$hrsd5s_b2 <- ifelse(is.na(CARTBIND$hrsd5s_b2), CARTBIND$hrsd5s_b1, CARTBIND$hrsd5s_b2)
CARTBIND$hrsd6s_b2 <- ifelse(is.na(CARTBIND$hrsd6s_b2), CARTBIND$hrsd6s_b1, CARTBIND$hrsd6s_b2)
CARTBIND$hrsd7s_b2 <- ifelse(is.na(CARTBIND$hrsd7s_b2), CARTBIND$hrsd7s_b1, CARTBIND$hrsd7s_b2)
CARTBIND$hrsd8s_b2 <- ifelse(is.na(CARTBIND$hrsd8s_b2), CARTBIND$hrsd8s_b1, CARTBIND$hrsd8s_b2)
CARTBIND$hrsd9s_b2 <- ifelse(is.na(CARTBIND$hrsd9s_b2), CARTBIND$hrsd9s_b1, CARTBIND$hrsd9s_b2)
CARTBIND$hrsd10s_b2 <- ifelse(is.na(CARTBIND$hrsd10s_b2), CARTBIND$hrsd10s_b1, CARTBIND$hrsd10s_b2)
CARTBIND$hrsd11s_b2 <- ifelse(is.na(CARTBIND$hrsd11s_b2), CARTBIND$hrsd11s_b1, CARTBIND$hrsd11s_b2)
CARTBIND$hrsd12s_b2 <- ifelse(is.na(CARTBIND$hrsd12s_b2), CARTBIND$hrsd12s_b1, CARTBIND$hrsd12s_b2)
CARTBIND$hrsd13s_b2 <- ifelse(is.na(CARTBIND$hrsd13s_b2), CARTBIND$hrsd13s_b1, CARTBIND$hrsd13s_b2)
CARTBIND$hrsd14s_b2 <- ifelse(is.na(CARTBIND$hrsd14s_b2), CARTBIND$hrsd14s_b1, CARTBIND$hrsd14s_b2)
CARTBIND$hrsd15s_b2 <- ifelse(is.na(CARTBIND$hrsd15s_b2), CARTBIND$hrsd15s_b1, CARTBIND$hrsd15s_b2)
CARTBIND$hrsd16s_b2 <- ifelse(is.na(CARTBIND$hrsd16s_b2), CARTBIND$hrsd16s_b1, CARTBIND$hrsd16s_b2)
CARTBIND$hrsd17s_b2 <- ifelse(is.na(CARTBIND$hrsd17s_b2), CARTBIND$hrsd17s_b1, CARTBIND$hrsd17s_b2)
CARTBIND$hrsd_total_b2 <- ifelse(is.na(CARTBIND$hrsd_total_b2), CARTBIND$hrsd_total_b1, CARTBIND$hrsd_total_b2)

# organize data
#
# Sex:
# orignial codes
# FOURD: 1 = Male; 2 = Female; 3 = Other; 4 = Prefer not to answer
# CARTBIND: 1=Female; 2=Male; 3=Unspecified, 9999=Unknown
# New codes
# 1=Female; 2=Male; 9999=Unknown
#
# Race:
# Orignial codes
# FOURD: 1 = White; 2 = Black; 3 = Asian; 4 = American Indian or Alaska native; 5 = Native Hawaiian or Other Pacific Islander; 6 = Other; 7 = Prefers not to answer
# CARTBIND: 1=American Indian/Native Alaskan, 2=Asian, 3=Black/African American, 4=White, 5=More than one race, 9996=Other, 9998= Prefer not to answer, 9999=Unknown
# New codes
# 1 = White; 2 = Black; 3 = Asian; 4 = American Indian or Alaska native; 5 = Other; 9999 = Unkown
#
# edu
# convert catbind data into education in years
# benzo
# 0=No; 1=Yes
# antidep
# 0=No; 1=Yes
# ANTIDEP_COMB
# 0=No; 1=Yes
# past_ect_yes_no
# 0=No; 1=Yes
# current psycho therapy yes no
# 0=No; 1=Yes

FOURD_renamed <- FOURD %>% 
      select(
        subj_id, AGE, SEX, RACE, YRS_EDUC, BENZO, ANTIDEP, 
        ANTIDEP_COMB, past_ect_yesno, current_psyther_yesno,
        hrsd_total_b, total_madrs_b
      ) %>% rename(age = AGE, sex = SEX, ethnicity = RACE, educ = YRS_EDUC,
        benzo = BENZO, antidep = ANTIDEP, antidep.combintn = ANTIDEP_COMB
           ) %>% mutate(ethnicity = recode(ethnicity, `6` = 5)
           ) %>% mutate(ethnicity = recode(ethnicity, `7` = 9999)
           ) %>% mutate(sex = recode(sex, `1` = 2, `2` = 1, `3` = 9999, `4` = 9999)
                        )%>% mutate(site = "FOURD")

CARTBIND_renamed <- CARTBIND %>% 
       select(
        subj_id, age, sex, ethnicity, educ, benzo, antidep, `antidep combintn`, past_ect_yesno, current_psyther_yesno, hrsd_total_b2, total_madrs_b
      )%>% rename(
        antidep.combintn = `antidep combintn`,
        hrsd_total_b = hrsd_total_b2
      ) %>% mutate(
        sex = recode(sex, `3` = 9999)
      ) %>% mutate(
        ethnicity = recode(ethnicity, `4` = 1, `3` = 2, `2` = 3, `1` = 4, `9996` = 5, `9998` = 9999, `9999` = 9999)
      ) %>% mutate(
        educ = recode(educ,
          `1` = 0, `2` = 1, `3` = 2, `4` = 3, `5` = 4, `6` = 5, `7` = 6,
          `8` = 7, `9` = 8, `10` = 9, `11` = 10, `12` = 11, `13` = 12,
          `14` = 12, `15` = 12, `16` = 15, `17` = 15, `18` = 15,
          `19` = 16,  `20` = 18, `21` = 22, `22` = 22
        )
      ) %>% mutate(site = "CARTBIND")

df4table <- rbind(FOURD_renamed, CARTBIND_renamed)
colnames(df4table) <- c("Subject ID", "Age", "Sex", "Ethnicity", "Education (years)", "Benzodiazepine use", "Antidepressant use", "Antidepressant combination use", "Past ECT", "Current psychotherapy", "HAMD", "MADRS", "Site")
df4table <- df4table %>%
  mutate(Sex = recode(Sex,
                      `1` = "Female",
                      `2` = "Male",
                      `9999` = "Missing")
         ) 
  
df4table$Ethnicity <- factor(df4table$Ethnicity, levels = c(1,2,3,4,5,9999), labels = c("White", "Black/African American", "Asian", "American Indian/Alaska native", "Other", "Missing"))

# make table
summary_table <- df4table %>%
  select(Site, Age, Sex, Ethnicity, `Education (years)`, `Benzodiazepine use`, `Antidepressant use`, `Antidepressant combination use`, `Past ECT`, `Current psychotherapy`, HAMD, MADRS) %>%
  tbl_summary(
    by = Site,
    statistic = list(
      Age ~ "{mean} ({sd})",
      `Education (years)` ~ "{mean} ({sd})",
      HAMD ~ "{mean} ({sd})",
      MADRS ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    missing_text = "Missing",
    digits = all_continuous() ~ 2
  ) %>%
  add_p() %>%
  add_overall(col_label = "**Total sample**, N = {N}") %>% 
  bold_labels()

summary_table
```

## Get the value range

```{r}
work_dir <- "/Users/ChenXiao/Library/CloudStorage/OneDrive-Personal/Documents/scale_crosswalk/Analysis"

# current data
load(file.path(work_dir, "benchmarks_ALL_carryover.RData"))
df_subset <- df_rmse[, -c(3, 5, 7, 9, 11)]
row_mins_H2M <- apply(df_subset, 1, function(x) min(x, na.rm = TRUE))
row_maxs_H2M <- apply(df_subset, 1, function(x) max(x, na.rm = TRUE))
load(file.path(work_dir, "benchmarks_M2H_ALL_carryover.RData"))
df_subset <- df_rmse[, -c(3, 5, 7, 9, 11)]
row_mins_M2H <- apply(df_subset, 1, function(x) min(x, na.rm = TRUE))
row_maxs_M2H <- apply(df_subset, 1, function(x) max(x, na.rm = TRUE))
mins <- rbind(row_mins_H2M, row_mins_M2H)
maxs <- rbind(row_maxs_H2M, row_maxs_M2H)

# baseline data
load(file.path(work_dir, "benchmarks_ALL_carryover.RData"))
df_subset <- df_rmse[, -c(1, 2, 4, 6, 8, 10)]
row_mins_H2M <- apply(df_subset, 1, function(x) min(x, na.rm = TRUE))
row_maxs_H2M <- apply(df_subset, 1, function(x) max(x, na.rm = TRUE))
load(file.path(work_dir, "benchmarks_M2H_ALL_carryover.RData"))
df_subset <- df_rmse[, -c(1, 2, 4, 6, 8, 10)]
row_mins_M2H <- apply(df_subset, 1, function(x) min(x, na.rm = TRUE))
row_maxs_M2H <- apply(df_subset, 1, function(x) max(x, na.rm = TRUE))
mins <- rbind(row_mins_H2M, row_mins_M2H)
maxs <- rbind(row_maxs_H2M, row_maxs_M2H)
```
